Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-06 src/tex/ms.tex
move timescale text to methods, point to Appendix

We \rev{first} follow a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against \rev{the UV Threshold Hypothesis}.
Under \rev{this hypothesis} ($H_1$), the probability of an exoplanet having detectable biosignatures is zero if the \rev{\gls{NUV}} irradiation is less than the threshold, and it is equal to the (unknown) probability of \rev{life emerging and persisting}, $f_\mathrm{life}$, if \gls{NUV} exceeds the threshold for a sufficiently long period of time \rev{$\Delta T_\mathrm{min}$.}
Under the null hypothesis ($H_\mathrm{null}$), that probability simply is $f_\mathrm{life}$, that is, it does not correlate with the \gls{UV} flux.
\rev{
While we adopt $\Delta T_\mathrm{min} = \SI{1}{\mega\year}$, we find that increasing this timescale to \SI{100}{\mega\year} reduces the fraction of inhabited planets under $H_1$ by less than 10 \%, suggesting that our results are not highly sensitive to $\Delta T_\mathrm{min}$.
}

@@

Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of \glspl{EEC} that are both inhabited and exhibit detectable biosignatures at the time of observation is unknown \rev{and is represented by the term $f_\mathrm{life}$.
This encompasses the probability of life both emerging and persisting to produce detectable biosignatures.}
\rev{Due to our ignorance about its true value or even its order of magnitude, we draw $f_\mathrm{life}$ from a log-uniform prior probability distribution.}
Let us consider the probability to detect a biosignature $P(L)$, and let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_1$, there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that

@@

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To construct a test \rev{of} the UV~Threshold Hypothesis, we required that life occurs only on planets with sufficient past \gls{UV} irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we required this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All commonly investigated origins-of-life scenarios require water as a solvent;
we thus considered only rocky planets that may sustain liquid water on their surface, i.e., that occupy their host star's momentary \gls{HZ} during the above period, as well as at the epoch of observation.
To determine \gls{HZ} occupancy, we took into account the evolution of the host star's luminosity and \gls{HZ} boundaries.

>>>>

We \rev{first} follow a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against \rev{the UV Threshold Hypothesis}.
Under \rev{this hypothesis} ($H_1$), the probability of an exoplanet having detectable biosignatures is zero if the \rev{\gls{NUV}} irradiation is less than the threshold, and it is equal to the (unknown) probability of \rev{life emerging and persisting}, $f_\mathrm{life}$, if \gls{NUV} exceeds the threshold for a sufficiently long period of time \rev{$\Delta T_\mathrm{min}$.}
Under the null hypothesis ($H_\mathrm{null}$), that probability simply is $f_\mathrm{life}$, that is, it does not correlate with the \gls{UV} flux.

@@

Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of \glspl{EEC} that are both inhabited and exhibit detectable biosignatures at the time of observation is unknown \rev{and is represented by the term $f_\mathrm{life}$.
This encompasses the probability of life both emerging and persisting to produce detectable biosignatures.}
\rev{Due to our ignorance about its true value or even its order of magnitude, we draw $f_\mathrm{life}$ from a log-uniform prior probability distribution (but see Appendix~\ref{sec:appendix-flife-prior} for a discussion of the impact of different priors).}
Let us consider the probability to detect a biosignature $P(L)$, and let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_1$, there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that

@@

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To construct a test \rev{of} the UV~Threshold Hypothesis, we required that life occurs only on planets with sufficient past \gls{UV} irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we required this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
\rev{
We nominally adopt $\Delta T_\mathrm{min} = \SI{1}{\mega\year}$.
Under $H_1$, longer origins timescales have minimal impact on a generic transit survey but significantly decrease the fraction of inhabited planets around FGK stars, as explored in Appendix~\ref{sec:long-origins}.
}

All commonly investigated origins-of-life scenarios require water as a solvent;
we thus considered only rocky planets that may sustain liquid water on their surface, i.e., that occupy their host star's momentary \gls{HZ} during the above period, as well as at the epoch of observation.
To determine \gls{HZ} occupancy, we took into account the evolution of the host star's luminosity and \gls{HZ} boundaries.
